%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\articletitle{A Search Engine Backed by Internet-Wide Scanning} % The title of the article
\articlecitation{\cite{censys15}} % The BibTeX citation key from your bibliography

\datenotesstarted{November 03, 2018} % The date when these notes were first made
\docdate{\datenotesstarted; rev. \today} % The date when the notes were lasted updated (automatically the current date)

\docauthor{Jordan Myers} % Your name

%----------------------------------------------------------------------------------------

\pagestyle{myheadings} % Use custom headers
%\markright{\doctitle} % Place the article information into the header

%----------------------------------------------------------------------------------------
%	PRINT ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\thispagestyle{plain} % Plain formatting on the first page

\printtitle % Print the title

%----------------------------------------------------------------------------------------
%	ARTICLE NOTES
%----------------------------------------------------------------------------------------

\section*{Notes} % Unnumbered section
\begin{itemize}
	\item Continually scans the internet.
	\item Produces structured data about hosts and protocols by dissecting handshakes.
	\item Raw handshake data saved.
	\item Data is then further processed - validated and annotated with metadata, e.g. device model, software version.
	\item Data is collected by protocol, but grouped by host.
	\item Zmap performs host discovery; hosts seed application scanners (ZGrab) which produce structured JSON.
	\item ZTag takes ZGrab JSON output, transforms data and adds annotations, and produces JSON doc.
	\item MongoDB 2.6.7 and Apache Cassandra 2.1.2 NoSQL DBs were initially considered but were too slow, particularly when handling unchanged records.
	\item ZDb, a custom DB was developed. A wrapper for RocksDB with optimizations to avoid disk access when there are no changes to data. The GitHub repo for ZDb is now deprecated.
	\item Elasticsearch is used for search and reporting. \cite{Elasticsearch}
	\item A Google Cloud Datastore collection is used to store history for each host
\end{itemize}

